Fusion Moves for Correlation Clustering

### 2014-11-10 paper/egpaper_for_review.tex
update HC

\section{Energy Based Hierarchical Clustering}\label{sec:ehc}

Agglomerative hierarchical clustering (HC) is widely used
in graph / image segmentation
\cite{arbelaez_2006}.
In each step, the edge with the highest weight $w$ is
contracted (red edges in Fig.~\ref{fig:hc_alg}).
Doing so, parallel edges edges can occur.

Hierarchical clustering is fast, and 
due to the agglomeration of edge weights, 
{\color{red} hierarchical clustering is robust against noise}.
{\color{yellow} [ First most similar nodes are merged...]
In agglomerative clustering, weights of
parallel edges are merged into single edges.}
For image segmentation, the length
weighted mean is used to do this update [ref].

[We contrary on those works work directly on energy functions and that why ...]
We propose to use Energy Based Hierarchical Clustering (EHC) to find
solutions for correlation clustering.

To make EHC follow the energy, we propose 
the following update rule:
Whenever there are multiple edges between 
a pair of nodes, these edges are merged into a single edge
by summing up their weights, since we 
minimize the sum of the cut edges.
The algorithm stops if the highest edge weight is
smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
contraction leads to worse energies.

@@

But EHC is very fast, and can be used to initialize
CGC \cite{beier_2014_cvpr}. Excessive time in CGC
is spend in the \emph{cut phase} to solve the 
first 2 coloring on the complete graph.
As shown in ~\ref{sec:exp},
allowing CGC to start from the EHC solution
can improve performance drastically.

Common cluster distances
\begin{itemize}
\item Single-Link: Nearest Neighbor - their closest members.
\item Complete-Link: Furthest Neighbor - their furthest members.
\item Centroid: Distance between centroids
\item Group Average: average of all cross-cluster pairs.
\end{itemize}

%------------------------------------------------------------------------
\section{Correlation-Clustering-Fusion (CCF) Moves}\label{sec:cc_fm}
Motivation Using Fusion moves -> problem ambiguity

>>>>

\section{Energy Based Hierarchical Clustering}\label{sec:ehc}
Agglomerative hierarchical clustering (HC) is widely used
in graph / image segmentation~\cite{arbelaez_2006}.
In each step, the edge with the highest weight $w$ is
contracted (red edges in Fig.~\ref{fig:hc_alg}).
Doing so, parallel edges edges can occur.
In agglomerative clustering, weights of
parallel edges are merged into single edges.
For image segmentation, the length
weighted mean is used to do this update~\cite{arbelaez_2006}.

While we, contrary to~\cite{arbelaez_2006}, directly work on energies, we are interesting in an 
agglomeration with respect to our energy function.
For this we propose to use energy based agglomeration
withe the following update rule:
Whenever there are multiple edges between 
a pair of nodes, these edges are merged into a single edge
by summing up their weights, since we 
minimize the sum of the cut edges.
We call HC with this update method Energy base Hierarchical Clustering (EHC).

We stop EHC if the highest edge weight is
smaller or equal to zero  (green edge in Fig.~\ref{fig:hc_alg}). Any further edge
contraction leads to worse energies.

% Hierarchical clustering is fast, and 
% due to the agglomeration of edge weights, 
% {\color{red} hierarchical clustering is robust against noise}.
% {\color{yellow} [ First most similar nodes are merged...]
% In agglomerative clustering, weights of
% parallel edges are merged into single edges.}
% For image segmentation, the length
% weighted mean is used to do this update [ref].

% [We contrary on those works work directly on energy functions and that why ...]
% We propose to use Energy Based Hierarchical Clustering (EHC) to find
% solutions for correlation clustering.

% To make EHC follow the energy, we propose 
% the following update rule:
% Whenever there are multiple edges between 
% a pair of nodes, these edges are merged into a single edge
% by summing up their weights, since we 
% minimize the sum of the cut edges.
% The algorithm stops if the highest edge weight is
% smaller or equal to zero  (green edge in fig. ~\ref{fig:hc_alg}). Any further edge
% contraction leads to worse energies.

@@

But EHC is very fast, and can be used to initialize
CGC~\cite{beier_2014_cvpr}. Excessive time in CGC
is spend in the \emph{cut phase} to solve the 
first 2 coloring on the complete graph.
As shown in Sec.~\ref{sec:exp},
allowing CGC to start from the EHC solution
can improve performance drastically.

% Common cluster distances
% \begin{itemize}
% \item Single-Link: Nearest Neighbor - their closest members.
% \item Complete-Link: Furthest Neighbor - their furthest members.
% \item Centroid: Distance between centroids
% \item Group Average: average of all cross-cluster pairs.
% \end{itemize}

%------------------------------------------------------------------------
\section{Correlation-Clustering-Fusion Moves}\label{sec:cc_fm}
Motivation Using Fusion moves -> problem ambiguity
